Mining Scenario/Transaction Pairs HW/SW Co-verification Using Symbolic Execution

### 2017-04-03 verifox.tex
Approach 1 description complete

\subsection{Path-based Symbolic Execution}
We have developed a symbolic execution tool, \verifox, 
for FW-HW co-verification of IP level and SoC level designs. 
Given a program netlist model, $\mathcal{PN}$, a scenario, 
$\mathcal{S}$, and a property expressed as $\mathit{assert}(c)$ 
(where $c$ is a condition stated in terms of variables in $\mathcal{PN}$)
as input, \verifox performs path-based exploration of $\mathcal{PN}$ 
to automatically infer {\em scencario/transaction} pairs and check their validity 
using backend solvers. If the condition $c$ does not hold, 
then $\mathcal{PN}$ is said to have violated the property.

\Omit{
explores only those FW-HW interactions
that are relevant to $\mathcal{S}$. \verifox

\verifox takes a C program as an input, where 
the properties of interest are specified using 
statements in the code. Here, $c$ is a condition 
stated in terms of program variables that we 
want to hold at the point where the assertion occurs. 
}

\Omit{
 that performs 
path-based exploration of a unified FW-HW model, 
$\mathcal{PN}$ to automatically check the validity of the 
relevant {\em scencario/transaction} pairs of the FW-HW interactions.
}
\Omit {
\verifox performs depth-first exploration 
of program paths with aggressive pruning strategy  
with certain optimizations
that makes it suitable for verifying hardware designs. 
A hardware circuit having its 
behaviour specified in a manner similar to state machine, would usually
be translated into a program that has a large number of control-flow paths with
only tiny fractions of them being feasible. 
}
A typical path-based symbolic execution engine might explore 
a path until it come to an $\mathit{assert}(c)$ statement.
This whole path can then be posed as a query to a SAT solver to see if the 
assertion is violated at that point. If the path is infeasible, the assertion
holds trivially. If a large number of paths are infeasible, symbolic 
execution may waste time exploring them. \verifox employs 
an eager infeasibility check to prune infeasible paths, 
as well as incremental encoding that makes
it easier for the underlying SAT solver. 
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{symex}{Symex}
%\SetKwFunction{assert}{assert}
\SetKwFunction{put}{put}
\SetKwFunction{get}{get}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{Safe}
\SetKwData{unsafe}{Unsafe}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
\Input{Program Netlist $\mathcal{PN}$ with properties specified with $assert(c)$, scenario specified with $assume(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
\tcc{The initial state}
$S_0 \leftarrow I(x)$ \nllabel{algline:init}\;
$stmt \leftarrow $ first statement \;
$worklist.put(\tuple{S_0,stmt})$ \;
\While{\KwNot $worklist.empty()$}
{
	$\tuple{S,stmt} \leftarrow worklist.get()$ \;
	\uIf{$stmt$ is an $assume(c)$ \nllabel{algline:assume}}
           {
			$stmt \leftarrow $ statement after $assume(c)$ \;
			\lIf{$isFeasible(S\wedge c)$}{$worklist.put(\tuple{S\wedge c,stmt})$}

@@

	}
	\return \safe \;
}
\end{small}
\caption{Working of \textsc{verifox}\label{Alg:verifox}}
\end{algorithm2e}

\Omit{
, in which every time a branch or an assumption
is encountered, a feasibility check is made to prune away infeasible 
paths as early as possible. }
\vspace{-4mm}
\algref{verifox} shows the overall algorithm of \verifox. States mentioned
in the algorithm are all symbolic states, which are quantifier-free predicates characterizing
a set of program states. 
Symbolic execution starts with an initial symbolic state $I(x)$, is a quantifier-free predicate
over program variables $x$, and the first statement $\mathit{stmt}$ to be executed.  Note that we assume all program variables
have finite bit-width and thus can be represented as bit-vectors.
Every statement acts as a state transformer during the symbolic execution. $\mathit{worklist}$ 
maintains the set of symbolic states, along with the corresponding
$\mathit{stmt}$ that should execute next. Assumptions can be specified in the program 
using $\mathit{assume}(c)$ statements, where $c$ is the condition expressed in terms 
of program variables. Assumptions restrict the search to only those
states for which the condition $c$ holds at the program point where $\mathit{assume}(c)$ is encountered.
For example, suppose $(x!=0)$ characterizes the set of states that has been discovered to be
reachable so far by a verification tool. Here, $x$ is a program variable.
Upon encountering $\mathit{assume}(x>0)$, the 
set of states reachable at the point of assumption is shrunk to only those that
satisfy $(x>0)$. A user can specify assumptions to restrict
the verification to only certain regions of the program's state space.

>>>>

\textbf{Step 4: Mining Scenario/Transaction Pairs Using Symbolic Execution}
Given a co-verification model, $\mathcal{M}_{seq}$, a scenario, 
$\mathcal{S}$, and a property expressed as $\mathit{assert}(c)$ 
(where $c$ is a condition stated in terms of variables in $\mathcal{M}_{seq}$)
as input, \verifox performs path-based exploration of $\mathcal{M}_{seq}$ 
to automatically infer {\em scencario/transaction} pairs and check their validity 
using backend solvers. If the condition $c$ does not hold, 
then $\mathcal{M}_{seq}$ is said to have violated the property.

A typical path-based symbolic execution engine might explore 
a path until it come to an $\mathit{assert}(c)$ statement.
This whole path can then be posed as a query to a SAT solver to see if the 
assertion is violated at that point. If the path is infeasible, the assertion
holds trivially. If a large number of paths are infeasible, symbolic 
execution may waste time exploring them. \verifox employs 
an eager infeasibility check to prune infeasible paths, 
as well as incremental encoding that makes
it easier for the underlying SAT solver. 
\begin{algorithm2e}[t]
\DontPrintSemicolon
\SetKwFunction{symex}{Symex}
%\SetKwFunction{assert}{assert}
\SetKwFunction{put}{put}
\SetKwFunction{get}{get}
\SetKwFunction{print}{print}
\SetKwFunction{return}{return}
%\SetKwFunction{assume}{assume}
%\SetKwFunction{isf}{isFeasible}
\SetKwData{safe}{Safe}
\SetKwData{unsafe}{Unsafe}
\SetKwInOut{Input}{input}
\SetKwInOut{Output}{output}
\SetKw{KwNot}{not}
\begin{small}
  \Input{Co-verification Model $\mathcal{M}_{seq}$ with properties specified with $assert(c)$, scenario specified with $assume(c)$}
\Output{The status (\safe or \unsafe) and a counterexample if \unsafe}
\tcc{The initial state}
$S_0 \leftarrow I(x)$ \nllabel{algline:init}\;
$stmt \leftarrow $ first statement \;
$worklist.put(\tuple{S_0,stmt})$ \;
\While{\KwNot $worklist.empty()$}
{
	$\tuple{S,stmt} \leftarrow worklist.get()$ \;
	\uIf{$stmt$ is an $assume(c)$ \nllabel{algline:assume}}
           {
			$stmt \leftarrow $ statement after $assume(c)$ \;
			\lIf{$isFeasible(S\wedge c)$}{$worklist.put(\tuple{S\wedge c,stmt})$}

@@

	}
	\return \safe \;
}
\end{small}
\caption{Mine Scenario/Transaction Pair Using Symbolic Execution\label{Alg:verifox}}
\end{algorithm2e}

\Omit{
, in which every time a branch or an assumption
is encountered, a feasibility check is made to prune away infeasible 
paths as early as possible. }
%\vspace{-4mm}
\algref{verifox} shows the overall algorithm of \verifox. States mentioned
in the algorithm are all symbolic states, which are quantifier-free predicates characterizing
a set of program states. 
Symbolic execution starts with an initial symbolic state $I(x)$, is a quantifier-free predicate
over program variables $x$, and the first statement $\mathit{stmt}$ to be executed.  Note that we assume all program variables
have finite bit-width and thus can be represented as bit-vectors.
Every statement acts as a state transformer during the symbolic execution. $\mathit{worklist}$ 
maintains the set of symbolic states, along with the corresponding
$\mathit{stmt}$ that should execute next. Assumptions can be specified in the program 
using $\mathit{assume}(c)$ statements, where $c$ is the condition expressed in terms 
of program variables. Assumptions restrict the search to only those
states for which the condition $c$ holds at the program point where $\mathit{assume}(c)$ is encountered.
For example, suppose $(x!=0)$ characterizes the set of states that has been discovered to be
reachable so far by a verification tool. Here, $x$ is a program variable.
Upon encountering $\mathit{assume}(x>0)$, the 
set of states reachable at the point of assumption is shrunk to only those that
satisfy $(x>0)$. A user can specify assumptions to restrict
the verification to only certain regions of the program's state space.
